Procurement Dynamics: Analyzing Federal Contract Awards to Microsoft

### 2024-11-26 paper/paper.qmd
Update paper

@@

## Model Validation?

@@

##

@@

The model assumes a linear relationship between the independent variables and the dependent variable. However, procurement dynamics may be more complex, with non-linear interactions between variables. [The model categorizes contract types and buyers into broad groups, which may oversimplify the true diversity of contracts awarded.

@@

## Next Steps

@@

1. Data Sources and Structure:

@@

2. Data Integration and Challenges:

@@

3. Solicitation Methods and Contract Types:

>>>>

### Model Justification
We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

## Model Validation [REMOVE?]

@@

## Data

The completeness and reliability of the data. For the missing or erroneous records, despite the data cleaning process, introduce bias and distort the findings.

Since the data of the procurement contracts awarded to Microsoft in Canada is between 2020 and 2024 (up to September), the analysis provides a snapshot of recent procurement trends during this period. However, the data do not capture longer-term patterns or emerging shifts in procurement policies.

@@

The model assumes a linear relationship between the independent variables and the dependent variable. However, procurement dynamics may be more complex, with non-linear interactions between variables. The model categorizes contract types and buyers into broad groups, which may oversimplify the true diversity of contracts awarded.

@@

## Weaknesses and Next Steps

@@

### Data Sources and Structure

@@

### Data Integration and Challenges:

@@

### Solicitation Methods and Contract Types:
